Farley et al. 2024

### 2025-01-10 IndividualStudies/SF_2024.qmd
Smoothing site architecture

---
title: "Farley et al. 2024"
format: 
  html:
    embed-resources: true
standalone: true
---

@@

@@

## Publication information

**Title:** Trifunctional Sphinganine: A New Tool to Dissect Sphingolipid Function

**Authors:** Scotland E. Farley, Frank Stein, Per Haberkant, Fikadu G. Tafesse, Carsten Schultz*

(* corresponding: <schulcar@ohsu.edu>{target="_blank"})

**Date published:**

**Journal, ISSN:** [ACS Chemical Biology](https://pubs.acs.org/doi/10.1021/acschembio.3c00554){target="_blank"}, 1554-8929, 1554-8937

**DOI:** <https://doi.org/10.1021/acschembio.3c00554>{target="_blank"}

@@

:::{.border}
```{r, echo=FALSE}
#| fig-cap: ""

@@

>>>>

---
title: "Farley et al. 2024"
subtitle: "Trifunctional Sphinganine: A New Tool to Dissect Sphingolipid Function"
format: 
  html:
    embed-resources: true
standalone: true
---

@@

write.csv(x = SF_2024_data, file = "DataTables/SF_ACS-Chem-Bio_2024_download.csv")

@@

Scotland E. Farley, Frank Stein, Per Haberkant, Fikadu G. Tafesse, Carsten Schultz*

Correspondence: <schulcar@ohsu.edu>{target="_blank"}

2024-02-16

[ACS Chemical Biology](https://pubs.acs.org/doi/10.1021/acschembio.3c00554){target="_blank"}

<https://doi.org/10.1021/acschembio.3c00554>{target="_blank"}

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: ""

@@

## Data download

{{< downloadthis DataTables/SF_ACS-Chem-Bio_2024_download.csv dname="SF_ACS-Chem-Bio_2024">}}
